---
title: 'Steal like an Rtist: Creative Coding in R'
subtitle: '02 - Homage to the Square Exercise 1'
output: html_document
---

# Exercise 1

## Part 1

Update the function `make_homage()` to take a `seed` argument, and set the seed in the body of the function

```{r ex-1-1}
library(ggplot2)
library(dplyr)

make_homage <- function(colors = c("#5A9CBA", "#919EA3", "#F1EFDF", "#F5BB1D")) {
  tribble(
    ~x0, ~y0, ~size,
    0, 0, 10,
    1, 0.5, 8,
    2, 1, 6,
    3, 1.5, 4
  ) %>%
    mutate(
      x1 = x0 + size,
      y1 = y0 + size,
      color = sample(colors, size = 4)
    ) %>%
    ggplot() +
    geom_rect(aes(
      xmin = x0, xmax = x1,
      ymin = y0, ymax = y1,
      fill = color
    )) +
    scale_fill_identity() +
    coord_fixed(expand = FALSE) +
    theme_void()
}
```

What happens if there is no value given to `seed` in the function?

## Part 2

Verify that running `make_homage()` with the same `seed` creates the same output, and that with a different seeds creates different outputs

```{r ex-1-2}
```

## Part 3

Share an output and the seed that created it in the GitHub discussion for this exercise! https://github.com/posit-conf-2023/creative-coding/discussions/2

```{r ex-1-3}
library(glue)

# seed <-
# homage <- 

ggsave(
  filename = glue("exercises/02-homage-to-the-square/ex1-homage-{seed}.png"),
  plot = homage,
  width = 5, height = 5
)
```
