---
title: 'Steal like an Rtist: Creative Coding in R'
subtitle: '02 - Homage to the Square Exercise 2'
output: html_document
---

# Exercise 2

## Part 1

Explore some of the sources discussed for finding color inspiration or a palette, and extract at least four colors from it.

Sources:

* Music, movies, books, furniture, architecture, nature, other artists!

Extracting colors from an image:

* https://mattdesl.github.io/colorgrab/

Palette sources:

* https://artsexperiments.withgoogle.com/artpalette/
* https://www.instagram.com/colours.cafe/
* https://coolors.co/generate
* https://www.color-hex.com/
* https://mycolor.space/

## Part 2

Update the function `make_my_homage()` below to take your palette as the default value of the `colors` argument

```{r ex-2-1}
library(ggplot2)
library(dplyr)

make_my_homage <- function(seed = 1, colors = c("#5A9CBA", "#919EA3", "#F1EFDF", "#F5BB1D")) {
  set.seed(seed)
  
  tribble(
    ~x0, ~y0, ~size,
    0, 0, 10,
    1, 0.5, 8,
    2, 1, 6,
    3, 1.5, 4
  ) %>%
    mutate(
      x1 = x0 + size,
      y1 = y0 + size,
      color = sample(colors, size = 4)
    ) %>%
    ggplot() +
    geom_rect(aes(
      xmin = x0, xmax = x1,
      ymin = y0, ymax = y1,
      fill = color
    )) +
    scale_fill_identity() +
    coord_fixed() +
    theme_void()
}
```

What happens if you try to use less than 4 colors?

## Part 3

Run the function `make_my_homage()` with a few different seeds and pick your favorite output

```{r ex-1-3}
```

## Part 4

Share the inspiration image or palette and an output in the GitHub discussion for this exercise: https://github.com/posit-conf-2023/creative-coding/discussions/3

```{r ex-2-4}
library(glue)

# seed <-
# homage <- 

ggsave(
  filename = glue("exercises/02-homage-to-the-square/ex2-homage-{seed}.png"),
  plot = homage,
  width = 5, height = 5, dpi = 300
)
```
