---
title: 'Steal like an Rtist: Creative Coding in R'
subtitle: 'Infinite Truchet by Roni Kaufman Exercise 3'
output: html_document
---

# Exercise 3

```{r setup}
library(dplyr)
library(ggplot2)
library(ggforce)
```

## Part 1

Run all of the code chunks in Part 1. This will give you access to the system `exercise_truchet_tiles()`.

```{r ex-3-1}
set_params <- function(x, y, sq_width, tile_type) {
  if (tile_type == 1) {
    tribble(
      ~x0, ~y0, ~start, ~end,
      x, y, 0, pi / 2,
      x + sq_width, y, 3 * pi / 2, 2 * pi,
      x + sq_width, y + sq_width, pi, 3 * pi / 2,
      x, y + sq_width, pi / 2, pi
    ) %>%
      mutate(num_arcs = c(3, 4, 3, 4))
  } else if (tile_type == 2) {
    tribble(
      ~x0, ~y0, ~start, ~end,
      x, y, 0, pi / 2,
      x + sq_width, y, 3 * pi / 2, 2 * pi,
      x + sq_width, y + sq_width, pi, 3 * pi / 2,
      x, y + sq_width, pi / 2, pi
    ) %>%
      mutate(num_arcs = c(5, 2, 5, 2))
  }
}
```


```{r ex-3-2}
exercise_truchet_tiles <- function(color1, color2, seed) {
  ncol <- 4
  nrow <- 4
  sq_width <- 15
  max_num_arcs <- 5

  set.seed(seed)

  grid <-
    expand_grid(
      y = seq(from = 0, by = sq_width, length.out = ncol),
      x = seq(from = 0, by = sq_width, length.out = nrow)
    ) %>%
    mutate(tile_type = sample(c(1, 2), size = n(), replace = TRUE))

  params_grid <-
    map_dfr(
      1:nrow(grid),
      function(i) {
        set_params(
          x = grid$x[i],
          y = grid$y[i],
          sq_width = sq_width,
          tile_type = grid$tile_type[i]
        )
      }
    )

  color <- c(color1, color2)
  color_seq <- rep(color, length.out = max_num_arcs)

  output <-
    map_dfr(
      1:nrow(params_grid),
      function(i) {
        bind_cols(
          slice(params_grid, i),
          r0 = seq(from = 1, by = 2, length.out = params_grid$num_arcs[i]),
          r = seq(from = 2, by = 2, length.out = params_grid$num_arcs[i]),
          color = color_seq[1:params_grid$num_arcs[i]]
        )
      }
    )


  return(output)
}
```


## Part 2

Within directory `exercises/05-infinite-truchet/` there is an image named `luft_13_roni.png`. This is from the Luft project, another truchet tile project created by Roni Kaufman. 

Navigate to https://mattdesl.github.io/colorgrab/ and drag and drop the image to the website. Use the colorgrab website to select two colors from the image to use in your system. Copy the hexcodes. 

Pass the hexcodes for these colors to `color1=` and `color2=` for `exercise_truchet_tiles()`. Modify the seed to experiment with different outputs. Feel free to also change the background color in `panel.background`.

```{r ex-3-3}
output_grid <-
  exercise_truchet_tiles(color1, color2, seed)
```

```{r ex-3-4}
output_grid %>%
  ggplot() +
  geom_arc_bar(aes(
    x0 = x0,
    y0 = y0,
    start = start,
    end = end,
    r0 = r0,
    r = r,
    fill = color,
    color = color
  )) +
  coord_fixed() +
  scale_fill_identity() +
  scale_color_identity() +
  theme_void() +
  theme(
    panel.background =
      element_rect(
        fill = "#050505",
        color = "#050505"
      )
  )
```


Save your image using `ggsave()` code provided and share on GitHub discussion board: https://github.com/posit-conf-2023/creative-coding/discussions/12

```{r ex-3-5}
ggsave(
  filename = "ex3-piece.png",
  plot = last_plot(),
  width = 5, height = 5
)
```
