---
title: 'Steal like an Rtist: Creative Coding in R'
subtitle: '03 - o.T. (carré noir) by Vera Molnár Exercises'
output: html_document
---

# Exercise 1

## Part 1

Open `exercises/03-ot/letters` - there are 6 letters in there. Select one and draw out the letter on your graphing paper.

Label all the vertices of the shape with the coordinates. Reminder, minimum value for x and y coordinates should be 0 and maximum should be 1. 

## Part 2

```{r ex-packages}
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
```

Create a `tribble()` and save it to output `letter_tribble` with the coordinates of the letter you selected. If you are having difficulty determining the coordinates, the coordinate solutions for each letter is in `exercises/03-ot/letters_solutions`.

```{r ex-1-1}
```

Confirm your coordinates are correct by running the following code chunk.

```{r ex-1-1}
ggplot(data = letter_tribble) +
  geom_polygon(
    aes(
      x = x,
      y = y
    )
  ) +
  coord_fixed()
```

## Part 3

Create a new function, `create_letter()` that takes `x0` and `y0` as arguments and moves the shape according to those arguments. See code/03-ot.R lines 55 through 68 for an example, if needed.

```{r ex-1-2}
```

Plot your shape at the x0 and y0 of your choosing by updating the `x0` and `y0` arguments in the `create_letter()` function. 

```{r ex-1-3}
plotted_letter <- create_letter() %>%
  ggplot() +
  geom_polygon(aes(
    x = x,
    y = y
  )) +
  coord_fixed()

plotted_letter
```

Share a picture of your output in the Github discussion for this exercise: https://github.com/posit-conf-2023/creative-coding/discussions/4

```{r ex-1-4}
ggsave(
  filename = "ex1-shape.png",
  plot = plotted_letter,
  width = 5, height = 5
)
```

Save your file when you are done with Exercise 1.

# Exercise 2

If you closed the file after the previous exercise, you may need to first re-run the code chunks from Exercise 1.

Run the code chunk below to have access to the `initiate_rotate_shape()` function.

```{r ex-2-1}
rotate_shape <- function(data, x0, y0, degrees, shape_width) {
  if (degrees == 90) {
    data %>%
      mutate(
        x = x - x0,
        y = y - y0
      ) %>%
      mutate(
        x_new = y,
        y_new = -x
      ) %>%
      mutate(
        x = x_new + x0,
        y = y_new + y0 + shape_width
      )
  } else if (degrees == 180) {
    data %>%
      mutate(
        x = x - x0,
        y = y - y0
      ) %>%
      mutate(
        x_new = -x,
        y_new = -y
      ) %>%
      mutate(
        x = x_new + x0 + shape_width,
        y = y_new + y0 + shape_width
      )
  } else if (degrees == 270) {
    data %>%
      mutate(
        x = x - x0,
        y = y - y0
      ) %>%
      mutate(
        x_new = -y,
        y_new = x
      ) %>%
      mutate(
        x = x_new + x0 + shape_width,
        y = y_new + y0
      )
  } else if (degrees == 0) {
    data
  }
}

initiate_rotate_shape <- function(x0, y0, degrees, shape_width) {
  output <- create_letter(x0 = x0, y0 = y0) %>%
    rotate_shape(
      x0 = x0,
      y0 = y0,
      degrees = degrees,
      shape_width = shape_width
    )

  return(output)
}
```

## Part 1

Experiment with changing the `x0`, `y0`, and the `degrees` argument within `initiate_rotate_shape()` to rotate and move your letter.

What happens if you change `shape_width` to be greater or smaller than 1? Why does this happen?

```{r ex-2-2}
# Change x0, y0, degrees here
# x0 <-
# y0 <-
# degrees <-
shape_width <- 1

rotated_shape <- initiate_rotate_shape(
    x0 = x0,
    y0 = y0,
    shape_width = shape_width,
    degrees = degrees
  )

ggplot(data = rotated_shape) +
  geom_polygon(aes(
    x = x,
    y = y
  )) +
  geom_point(
    aes(
      x = x0,
      y = y0
    ),
    color = "red"
  ) +
  coord_fixed()
```

Remember to save your file when you are done with the exercise.

# Exercise 3

If you closed the file after the previous exercise, you may need to first re-run the code chunks from Exercise 1 and 2.

## Part 1

Run the code chunk that contains the `make_exercise_molnar()` function which encompasses the whole system. It has been modified to take two additional arguments: `degree_pattern_options=` & `degree_sample_size=`. 

```{r ex-3-1}
make_exercise_molnar <-
  function(seed, degree_pattern_options, degree_sample_size) {
    set.seed(seed)

    ncol <- 10
    nrow <- 10
    shape_width <- 1
    perimeter_width <- shape_width + .25

    degree_pattern <- sample(degree_pattern_options, size = degree_sample_size, replace = TRUE)

    grid <-
      expand_grid(
        x = seq(0, by = perimeter_width, length.out = nrow),
        y = seq(0, by = perimeter_width, length.out = ncol)
      ) %>%
      mutate(y = if_else(x >= 5 * perimeter_width,
        y + perimeter_width / 2,
        y
      ))

    degree_pattern_exp <- rep(degree_pattern,
      length.out = nrow(grid)
    )

    output <-
      map_dfr(
        1:nrow(grid),
        function(i) {
          bind_cols(
            group = i,
            initiate_rotate_shape(
              x = grid$x[i],
              y = grid$y[i],
              degrees = degree_pattern_exp[i],
              shape_width = shape_width
            )
          )
        }
      )

    return(output)
  }
```

Pass a vector of degree options (ex. `c(0, 90, 180, 270)`) to `degree_pattern_options=` and a number for the `degree_sample_size=`. Remember to set a seed for your output to be reproducible. 

Suggestions: 1) You do not have to use all of 0, 90, 180, and 270, and 2) You could make the sample size small or large. 

If you have additional time you can experiment with colors in the `fill=` and `color=` in `geom_polygon()` and in the `plot.background` in `theme()`

```{r ex-3-2}
final_output <-
  make_exercise_molnar(
    degree_pattern_options = ,
    degree_sample_size = ,
    seed =
    )

final_output %>%
  ggplot() +
  geom_polygon(
    aes(
      x = x,
      y = y,
      group = group
    ),
    fill = "#1a1617",
    color = "#1a1617"
  ) +
  coord_fixed() +
  theme_void() +
  theme(
    plot.background =
      element_rect(
        fill = "#e8e6e5",
        color = "#e8e6e5"
      )
  )
```

## Part 2

Share a picture of your output in the Github discussion for this exercise: https://github.com/posit-conf-2023/creative-coding/discussions/6

```{r ex-3-3}
ggsave(
  filename = "ex3-piece.png",
  plot = last_plot(),
  width = 5, height = 5
)
```
